---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Adam Hubbell"
date: "8/26/2019"
output: 
  html_document: 
    fig_height: 8
    fig_width: 8
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code.)

datasaurus dozen has 1846 rows and 3 columns

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
dino_data's r value is -0.0645

### Exercise 3

```{r filter-star}
star_data <- datasaurus_dozen %>% 
   filter(dataset == "star")
```

```{r plot-star}
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
   geom_point()
```

The star plot's points seems to congregate in each acute angle of the star

```{r cor-star}
star_data %>% 
   summarize(r = cor(x, y))
```
The star data's r value is -0.0630

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r filter-circle}
circle_data <- datasaurus_dozen %>% 
   filter(dataset == "circle")
```

```{r plot-circle}
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
   geom_point()
```

The circle plot looks more eliptical than circular. 

```{r cor-circle}
circle_data %>% 
   summarize(r = cor(x, y))
```
The circle data's r value is -0.0683

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)
```{r plot-all}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r summerize data}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```